High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-05-30 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

The observed SED is compared with the model in Fig.~\ref{fig:SED}. From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{sub}$), i.e. an inner disc, as it was crucial to fit the 5--10\,$\micron$ range. On the other hand, the observed central and compact signal in the ALMA observation cannot be explained with the hypothesis of thermal emission from large grains in the inner disc. Following the mass estimates in Section~\ref{sec:Observations}, the millimetre-sized dust needed reaches $\sim$18 times larger surface densities than in the gas, resulting in a large excess at 10$\,\micron$ that does not match the data. Meanwhile, the decision of employing the three-ringed structure (i.e. add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 4--6\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.

>>>>

The observed SED is compared with the model in Fig.~\ref{fig:SED}. From the similarity with the data, we propose that there has to be a small-grain population close to the stars down to 0.3\,au ($R_{sub}$), i.e. an inner disc, as it was crucial to fit the 5--10\,$\micron$ range. Meanwhile, the decision of employing the three-ringed structure for the small dust (i.e. add Ring5 to the observed structure) relies on the fact that the SED needed a thin ring at a radius at $\sim$5\,au to have a proper fit around 10\,$\micron$, otherwise, instead of the distinct bump that is present, there would be a gap.
